Article Title

### 2019-02-13 doc/letter_editor.tex
needed to update ignore and restage

\begin{document}
\begin{letter}{Editor \\ \textit{PeerJ}}
  \opening{Dear Editor,}

  Please find enclosed the manuscript entitled ``Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})'' which we are submitting for consideration for the \textit{PeerJ}. This manuscript is authored by myself (Peter D Smits), Kenneth D Angielczyk, James F Parham, and Bryan L Stuart. We believe our analysis and results are of interest to the community as we present a non-standard approach for evaluating the intensity of cryptic diversity and the efficacy of different classification schemes.

>>>>

\begin{document}
\begin{letter}{Editor \\ \textit{PLoS One}}
  \opening{Dear Editor,}

  Please find enclosed the manuscript entitled ``Ensemble approaches for estimating congruence between species delimitation and morphological variation: a case study using the Pacific Pond Turtle (\textit{Emys marmorata})'' which we are submitting for consideration for the \textit{PLoS One}. This manuscript is authored by myself (Peter D Smits), Kenneth D Angielczyk, James F Parham, and Bryan L Stuart. We believe our analysis and results are of interest to the community as we present a non-standard approach for evaluating the intensity of cryptic diversity and the efficacy of different classification schemes.
